### 2017-05-01 2017mergingmerges/section/05A-Benchmarks.tex
Update benchmark graphs

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
  symbolic y coords={Conduit, Pipes, Streaming, Ours, end},
	xlabel=Runtime (ms),
  xmin=0, xmax=360,
	enlargelimits=0.01,
	xbar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(360,Conduit) (310,Pipes) (235,Streaming) (160,Ours) (0,end) };
\end{axis}
\end{tikzpicture}
\caption{Runtime for append2; lower is faster.}
\label{fig:bench:append}
\end{figure}

\subsection{Append files}
The first file-based benchmark consists of appending two files, while counting the number of lines.
We have benchmarked against three Haskell streaming libraries: Conduit, Pipes, and Streaming.
\autoref{fig:bench:append} shows the runtimes for appending 1.8MB of data.
The absolute performance here is poor here because all are using line-buffered IO; in practice one would use chunked IO, but the overhead per chunk would be the same.

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
  symbolic y coords={Streaming, Conduit, Pipes, Ours, end},
	xlabel=Runtime (ms),
  xmin=0, xmax=1570,
	enlargelimits=0.01,
	xbar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(1570,Streaming) (980,Conduit) (940,Pipes) (590,Ours) (0,end) };
\end{axis}
\end{tikzpicture}
\caption{Runtime for partition; lower is faster.}
\label{fig:bench:part}
\end{figure}

>>>>

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
  symbolic y coords={Conduit, Pipes, Streaming, Ours, end},
	xlabel=Runtime (ms),
  xmin=0, xmax=290,
	enlargelimits=0.01,
	xbar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(282,Conduit) (270,Pipes) (168,Streaming) (86,Ours) (0,end) };
\end{axis}
\end{tikzpicture}
\caption{Runtime for append2; lower is faster.}
\label{fig:bench:append}
\end{figure}

\subsection{Append files}
The first file-based benchmark consists of appending two files, while counting the number of lines.
We have benchmarked against three Haskell streaming libraries: Conduit, Pipes, and Streaming.
\autoref{fig:bench:append} shows the runtimes for appending 1.8MB of data.
The absolute performance here is poor because all are using line-buffered IO; in practice one would use chunked IO, but the overhead per chunk would remain.

\begin{figure}
\begin{tikzpicture}
\begin{axis}[
  symbolic y coords={Streaming, Pipes, Conduit, Ours, end},
	xlabel=Runtime (ms),
  xmin=0, xmax=1200,
	enlargelimits=0.01,
	xbar interval=0.7,
  width=7.5cm, height=4.5cm,
	legend pos=north west,
]
\addplot coordinates {(1200,Streaming) (764,Pipes) (658,Conduit) (288,Ours) (0,end) };
\end{axis}
\end{tikzpicture}
\caption{Runtime for partition; lower is faster.}
\label{fig:bench:part}
\end{figure}
